# Python Extraction Code

```{r pysetup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, warning=FALSE)
library(reticulate)
library(lemon)
library(knitr)
library(kableExtra)
library(tidyverse)
library(DT)
```

The following data extraction and cleaning code is from `simulation.ipynb`. This file used to be where I did exploratory analysis of the data and tried some models.

The Python notebook is also used to generate a rudimentary config file, which I later added additional data to (note to self: don't run it or it will overwrite!). It seems that now Rmarkdown nicely integrates Python, [but the Reticulate package was only released in August 2018](https://cran.r-project.org/web/packages/reticulate/index.html). Oh well. I've put the Python code in here so technically, if I ran this notebook right this moment, it would do it all.

## Pre-processing

(Unix) Launch with

```
cd src
jupyter notebook
```

**Notes**

- `read_binary_solution` is able to read from Vida's outputs and turn it into a well/FP mapping. However I don't use it now because she doesn't map all of the wells. Instead I manually enter it from `Data for AU.xlsx`.
- Here we read in the Liquid Wells spreadsheet. My script manages to pick up at least 30 of the approx. 60 wells in here, but I manually copy/pasted the rest because it was too annoying.
- The network structure and parameters are read from a config spreadsheet, `config.xlsx`. I generate as much as I can automatically and then fill any gaps manually.

```{python, results="asis"}
import pandas as pd
import numpy as np
import seaborn as sns
from datetime import datetime, timedelta
import matplotlib.pyplot as plt
from matplotlib.colors import Normalize
from matplotlib.colorbar import ColorbarBase
from IPython.display import display, HTML
import itertools
import os
import pyjags
import warnings

base_year = '2000'    # numeric dates calculated from Jan-01
configpath = '../wairakei_data/config.xlsx'

def read_binary_solution(path='../wairakei_data/toy-network-v4.xlsm'):
    # read from Vida's toy model workbook
    xlfile = pd.ExcelFile(path)
    sheet = xlfile.parse('Full LP')
    sheet = sheet.loc[sheet.count(1)>50]  # arbitrary, anything works
    sheet = sheet.transpose()
    sheet.columns = ['used', 'combination']
    combinations = pd.DataFrame([x.split('-') for x in sheet.query('used==1')['combination']],
                               columns = ['well', 'fp'])
    combinations['well'] = 'wk' + combinations['well']
    combinations['fp'] = 'fp' + combinations['fp']
    return(combinations)

def myprint(df):
    display(HTML(df.to_html()))
    
def central(data, m=3.29):
    return data[abs(data - np.mean(data)) < m * np.std(data)]

def rename_wk(names):
    # fix 'WK' inconsistencies
    new = names.str.lower()
    new = new.str.replace("^[^\d]*", "wk")
    new = new.str.strip()
    return new
    
def datetime_to_numeric(my_datetime):
    # returns days since base_year-01-01.
    try:
        # datetime implem
        date_numeric = (my_datetime - datetime(int(base_year),1,1)) / timedelta(days=1)
    except:
        # numpy implem
        date_numeric = (my_datetime - np.datetime64(base_year)) / np.timedelta64(1, 'D')
    return date_numeric

# Check if Excel file is already in memory (loading is slow)
try:    xl
except: xl = pd.ExcelFile('../wairakei_data/Liquid wells (version 1).xlsx')
sheetlist = [x for x in xl.sheet_names if set(x) & set('FtT(L') == set()]
print("Sheets:", ', '.join(sheetlist))

# sheets to load data from
sheets = ['wk255', 'wk256']

dfs = []
for sheet in sheets:
    try:
        df = xl.parse(sheet)  # select well data
        df['well'] = sheet    # label data with well name
        dfs.append(df)
    except:
        print('Failed on sheet', sheet)
df = pd.concat(dfs)

df = df[['date', 'whp', 'mf', 'h', 'well']]           # only keep certain columns
df['well'] = rename_wk(df['well'])
df['mf'] = pd.to_numeric(df['mf'], errors='coerce')   # remove 'dummy' entries
df = df.dropna(subset=['date', 'whp', 'mf'])          # remove NA
df['date_numeric'] = datetime_to_numeric(df['date']) #  yrs since base_year
df = df.reset_index(drop=True)
wells = df['well'].unique()
print(df.head())

regression_df = df.reset_index(drop=True)
wells = regression_df['well'].unique()
print(wells)

# import and process data
try:    fpxl
except: fpxl = pd.ExcelFile('../wairakei_data/Data for AU.xlsx')
    
fpdf = pd.read_excel(fpxl, 'calculation', header=1, usecols="D:E, J:L, N:P")
fpdf = fpdf.rename(columns={"FP15": "well", "Unnamed: 1": "fp",
                            "hf": "hf_ip", "hg": "hg_ip", "hfg": "hfg_ip",
                            "hf.1": "hf_lp", "hg.1": "hg_lp", "hfg.1": "hfg_lp"})
 # make sure it has the necessary data
fpdf = fpdf[pd.to_numeric(fpdf['hf_ip'], errors='coerce').notnull()]
for col in ['well', 'fp']:
    fpdf[col] = fpdf[col].str.lower()
fpdf[fpdf.columns] = fpdf[fpdf.columns].apply(pd.to_numeric, errors='ignore')
print(fpdf.head())

def write_config(configpath):
    # only use if it gets lost. Will refresh file
    well_fp_map = pd.DataFrame({'well': ['wk27', 'wk242', 'wk247', 'wk253', 'wk254',
    'wk255', 'wk256', 'wk258', 'wk259', 'wk267', 'wk268', 'wk269', 'wk270', 'wk271', 'wk272'],
                                'fp':   ['fp1',  'fp14',  'fp15', 'fp16',  'fp16',
                                'fp15',  'fp15',  'fp16',  'fp16',  'fp16',  'fp16',
                                'fp15',  'fp15',  'fp14',  'fp14']},
                               columns=['well', 'fp'])
    fp_gen_map = pd.DataFrame({'fp':     ['abandoned', 'poi dry', 'direct ip', 'fp1',
                               'fp14', 'fp15', 'fp16', 'fp2', 'fp4', 'fp5', 'fp9-10'],
                               'gen_ip': [ None,       'POI',      None,       'WRK',
                               'WRK',  'THI',  'POI',  'WRK', 'WRK', 'WRK', 'WRK'   ],
                               'gen_lp': [ None,       'POI',      None,       'WRK',
                               'WRK',  'THI',  'POI',  'WRK', 'WRK', 'WRK', 'WRK'   ],
                               'gen_w':  [ None,        None,      None,       'BIN',
                               None,   None,   None,  'BIN', 'BIN', 'BIN', 'BIN'   ]},
                              columns=['fp', 'gen_ip', 'gen_lp', 'gen_w'])
    gen_constants = pd.DataFrame({'gen':    ['WRK', 'THI', 'BIN', 'POI' ],
                                  'ip':     [ True,  True,  False, True ],
                                  'lp':     [ True,  True,  False, True ],
                                  'bin':    [ False, False, True,  False],
                                  'factor': [ 9.2,   8.22,  178.9, 7.76]},  # m3/MW
                                 columns=['gen', 'ip', 'lp', 'bin', 'factor'])
                                 
    # find details of the last known operating conditions
    last_idx = regression_df.groupby('well')['date_numeric'].idxmax()
    operating_conditions = regression_df.iloc[last_idx][['well', 'whp', 'h']]

    # set constants (could use median)
    fp_constants = fpdf.groupby('fp').mean().reset_index()

    if os.path.exists(configpath):
        os.remove(configpath)
    config_writer = pd.ExcelWriter('../wairakei_data/config.xlsx')
    print("Writing config data to", configpath)
    configdata = {'well_fp_map': well_fp_map,
                  'fp_gen_map': fp_gen_map,
                  'operating_conditions': operating_conditions,
                  'fp_constants': fp_constants,
                  'gen_constants': gen_constants}
    for sheetname, df in configdata.items():
        df.to_excel(config_writer, sheetname, index=False)
    # config_writer.save() # Don't overwrite!
    return pd.ExcelFile(configpath)

try:
    config = pd.ExcelFile(configpath)
except FileNotFoundError:
    print("Warning: are you sure you want to overwrite the config file?")
#     config = write_config(configpath)

## Exploratory Analysis
import itertools

cmap = plt.get_cmap('viridis')
fig, (ax1, ax2) = plt.subplots(1,2, figsize=[14,4])
fig.tight_layout() #spreads out the plots

# left plot (not that useful tbh)
df.plot('date', 'whp', style='x', ax=ax1)
ax1.set_xlabel('date')
ax1.set_ylabel('whp')

# right plot (different colours represent time)
marker = itertools.cycle(['o', ',', '+', 'x', '*', '.'])
for well in wells:
    plt.scatter('whp', 'mf', c='date_numeric',
    data=df.loc[df['well']==well], marker=next(marker), label=well)
ax2.set_xlabel('whp')
ax2.set_ylabel('mf')
plt.legend()

plt.show()

## Set up regression data and create prediction frame for plotting
date_pred = np.arange(df['date'].min(), df['date'].max(),
        np.timedelta64(365*2, 'D').astype(datetime))
date_numeric_pred = datetime_to_numeric(date_pred)
whp_pred = np.linspace(0, 16, 1000)
well_pred = wells
pred = pd.DataFrame(list(itertools.product(date_numeric_pred, whp_pred, well_pred)),
                    columns=['date_numeric', 'whp', 'well'])
print(pred.head(3))

## Perform regression and prediction
from statsmodels.formula.api import ols

# Not conditioned on date
model1 = ols("mf ~ well * whp", data=df)
results1 = model1.fit()
pred['mf1'] = results1.predict(pred)

# Linear fit dependent on date
model2 = ols("mf ~ well * (whp + date_numeric)", data=df)
results2 = model2.fit()
pred['mf2'] = results2.predict(pred)

# Elliptic fit dependent on date
model3 = ols("np.power(mf,2) ~ well * (np.power(whp,2) + date_numeric)", data=df)
results3 = model3.fit()
pred['mf3^2'] = results3.predict(pred)
pred.loc[pred['mf3^2'] < 0, 'mf3^2'] = np.nan    # remove invalid results
pred['mf3'] = np.sqrt(pred['mf3^2'])

print(pred.head(3))

# ===============================================================
# Set up axes
# ===============================================================
# colors
cmap = plt.get_cmap('viridis')
indices = np.linspace(0, cmap.N, len(df))
my_colors = [cmap(int(i)) for i in indices]

# subplots
fig, (ax1, ax2, ax3, ax4) = plt.subplots(1, 4, figsize=[14,4],
        gridspec_kw={'width_ratios': [9,9,9,1]})
ax1.get_shared_y_axes().join(ax1, ax2, ax3)
ax1.set_ylim([0, 1000])
ax1.set_xlim(0, 16)
ax1.set_ylabel('Mass flow')
ax1.set_xlabel("Well head pressure")
ax1.set_title('$mf \sim whp$')
ax2.set_title('$mf \sim whp + date$')
ax3.set_title('$mf^2 \sim whp^2 + date$')

# create date colorbar
indices = np.linspace(0, cmap.N, len(date_pred))
my_colors = [cmap(int(i)) for i in indices]
norm = Normalize(np.min(df['date']).year, np.max(df['date']).year)
cb = ColorbarBase(ax4, cmap=cmap, norm=norm, orientation='vertical')
cb.set_label('Year')
linestyles = itertools.cycle(('-', '--', '-.', ':'))
marker = itertools.cycle(['o', ',', '+', 'x', '*', '.'])

# ===============================================================
# Plot data
# ===============================================================
# plot raw data points
for well in wells:
   mkr = next(marker)
   for ax in [ax1, ax2, ax3]:
       ax.scatter('whp', 'mf', c='date_numeric',
              data=df.loc[df['well']==well], marker=mkr, label=well)
 
# plot fitted curves
for well in wells:
    lty = next(linestyles)
    # model 1
    # 'data' argument filters the data to just the data from one well
    ax1.plot('whp', 'mf1', lty, data=pred[(pred['well']==well)])
   
    # models 2 & 3
    for i, date in enumerate(date_numeric_pred):
        # 'data' argument similar, for a specific prediction date in the loop
        ax2.plot('whp', 'mf2', lty,
        data=pred[(pred['well']==well) & (pred['date_numeric']==date)], c=my_colors[i])
        ax3.plot('whp', 'mf3', lty,
        data=pred[(pred['well']==well) & (pred['date_numeric']==date)], c=my_colors[i])
       
# show model selection criteria
for ax, result in zip([ax1, ax2, ax3], [results1, results2, results3]):
    ax.legend(['Adj $R^2$: %.2f' % result.rsquared_adj,
            'AIC: %.2f' % result.aic],
            handlelength=0, handletextpad=0, loc=1).legendHandles[0].set_visible(False)
             
plt.show()
```

## Preview Data 

Let's have a look at what we get out of the pre-processing.

We begin with the regression data.

```{r}
py$df %>% head(12) %>% datatable(caption="Well calibration data", options=list(scrollX=T))
```

Now, the flash plant operating conditions.

```{r}
py$fpdf %>% head(12) %>% 
  datatable(caption="Flash plant operational parameters", options=list(scrollX=T))
```

Here's a (deterministic) example of what we expect to get out - mass flow predictions per well. But we will use JAGS to get stochastic samples rather than this regression.

```{r, echo=FALSE}
# py$pred %>% head(12) %>% datatable(caption="Mass flow prediction demo")
py$pred %>% head(12) %>% kable(caption="Mass flow prediction demo") %>% 
  kable_styling %>% scroll_box(width="100%")
```
